\section*{Abstract}
The Navoy AI travel platform is a proprietary software solution that enables users to craft and book ultra personalized trips with seamless automated AI flow.
It leverages artificial intelligence to generate highly customized travel itineraries and provides enterprise-level API access for businesses.

To start off, I have two big roles to play.
\textbf{The first} one is to develop new features for the existing AI travel platform while continuously improving the user experience and personalization capabilities.
\textbf{The second} and the most important one is to migrate Navoy from a monolithic application to a \textbf{microservices} architecture in order to make it infinitely scalable. I also have to find the ideal environment to deploy my newly created microservices to, in order to ensure their intra-communication.

I start by breaking the application into various NestJS microservices, build the corresponding docker images then create a shared Helm package for the microservices. Second of all, I setup my own \textbf{self-managed Kubernetes cluster with MicroK8s and ansible scripts}, configure it appropriately to support the specific use-case, then deploy the application stack to both staging and production.

Lastly, using \textbf{GitLab's CI/CD pipelines} and also \textbf{GNU's Makefiles} allows me to automate the whole process from start to finish.
So that in the end, one commit on the main branch is enough to deliver my changes to the clients, which is the standard that \textbf{DevOps compliant} applications should follow.

\newpage
