\section*{Acknowledgments}
I would like to take a moment to thank all of those involved in finalizing this work, whether directly or indirectly.

% Thanking the Navoy team
My profound gratitude goes to the entire \textbf{Navoy team} for their warm welcome, invaluable support and for accompanying me throughout this wonderful journey.
Special thanks to the company CEO \textbf{Mr. Haroun Moula} who has been very involved with me almost daily throughout the long period of the internship, his trust in me has truly allowed me to come very far during this project.
I also appreciate my technical supervisor \textbf{Mr. Ala Tabene} for initially showing me the ropes and for his continuous guidance throughout the development process.
My deepest gratefulness also goes to the entire Navoy team for their huge efforts in contributing to making this startup a success, amongst other things, their input has truly been a huge source of knowledge for me and will be forevermore.

% Thanking the University supervisor
I also wish to acknowledge the great support of my university supervisor \textbf{Mr. Firas Khlil} for his assistance, availability and valuable spot-on advice.
His faith in me has truly allowed me to keep working on this project stress-free while confident this report will turn out better than initially intended.

My heartfelt appreciation goes to the jury members who agreed to evaluate my work and I hope they find it up to standard.
I equally thank all of the teachers of the IT Business School
(ITBS) who contributed to my education during these wonderful two and a half years.

\newpage
